Simulations of Ballot Polling Risk-Limiting Audits

### 2023-02-19 providence/sections/workload.tex
small changes

As an example, we consider the US Presidential contest in the 2016 Virginia statewide general election. This contest had a margin of $0.053$ between the two candidates with the most votes.
Analytical approximation of the expected audit behavior (quantities like expected total number of ballots sampled or total number of rounds) is challenging because the number of possible sequences of samples grows exponentially with the number of rounds. 
%A very rough approximation scheme is possible and may be useful when choosing round sizes in practice. We implement such a scheme, available at \cite{software}.
%We will use the more standard approach of simulations to give an example here.
Therefore we use the typical approach of simulations, again with risk limit $0.1$.

>>>>

As an example, we consider the US Presidential contest in the 2016 Virginia statewide general election. This contest had a margin of $0.053$ between the two candidates with the most votes.
Analytical approximation of the expected audit behavior (quantities like expected total number of ballots sampled or total number of rounds) is not straightforward. %challenging because the number of possible sequences of samples grows exponentially with the number of rounds. 
%A very rough approximation scheme is possible and may be useful when choosing round sizes in practice. We implement such a scheme, available at \cite{software}.
%We will use the more standard approach of simulations to give an example here.
Therefore we use the typical approach of simulations, again with risk limit $0.1$.
